### 2015-04-22 paper.tex
Use subplots fig for perf Re dep
Add figures

\begin{figure}[h]
\caption{{\bf Turbine Model Drawing.}
Drawing of the turbine with and without strut covers.}
\label{fig:turbine-drawing}
\end{figure}

@@

\begin{figure}[h]
\centering
%\includegraphics[clip,trim=0.01in 0 0 0,
%width=0.95\textwidth]{Figures/tank_cross_section}
\caption{Illustration of the experimental setup.}
\label{fig:exp-setup}
\end{figure}

@@

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/re_dep_cp}
\caption{{\bf Power Coefficient Reynolds Number Dependence.}
Power coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
\label{fig:cp-re-dep}
\end{figure}

>>>>

\begin{figure}[h]
\includegraphics[width=0.65\textwidth]{figures/turbine}
\caption{{\bf Turbine Model.}
Drawing of the turbine.}
\label{fig:turbine-drawing}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[clip,trim=0.01in 0 0 0,
width=\textwidth]{figures/tank_cross_section}
\caption{Illustration of the experimental setup.}
\label{fig:exp-setup}
\end{figure}

@@

Wake measurements were all performed at 1 m downstream, which corresponds to
$x/D = 0.93$. The cross-stream and vertical coordinates are shown in
Fig.~\ref{fig:coordinates}.

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/turbine_coordinate_system}
\caption{{\bf Coordinate system.} Wake measurement coordinate system and 
cross-stream/vertical coordinates. All dimensions are in meters.} 
\label{fig:coordinates}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/perf_re_dep}
\caption{{\bf Reynolds Number effects on performance.}
Power and drag coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
\label{fig:cp-re-dep}
\end{figure}
